Electro-Drop Bouncing in Low-Gravity

### 2018-08-08 doc/paper/aiptemplate.tex
added some new figures

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{../figures/apparatus0.pdf}
\label{apparatus}
\caption{Schematic representation of drop jump with return and rebound from an electrically charged superhydrophobic substrate. The characteristic time and length scales $t_c$ and $y_c$ describe the time of flight and apoapse associated with the drop trajectory.}
\end{figure}

@@

Because Equation \ref{gov_eqn_subs} behaves stiffly we integrate it using the \emph{netlib ODEPACK} library double-precision \verb|lsoda| integrator wrapped within the \verb|odeint| \emph{Scipy} \cite{oliphant_python_2007} module in Python. The optimization problem in this case is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned. The ill-conditioning arises due to the strong covariance between several of the model parameters, namely $q=q(V_d, E_0)$. The non-convexity of the problem implies that there are many local minima of the objective function. We use a gradient-free direct-search Nelder-Mead \cite{nelder_simplex_1965} algorithm implemented in \verb|scipy.optimize|. Nelder-Mead is relatively robust to noise and is thrifty with our computationally expensive function-calls. Experimental trajectory data is smoothed using a Savitsky-Golay filter \cite{savitzky_smoothing_1964} to improve the convergence characteristics of the optimizer. This filter is implemented in the \verb|scipy.signal| Python \emph{SciPy} module. We precondition the optimization problem by minimizing $\ln(\chi^2)$ and using a naive $\sim \mathcal{O}(1)$ scaling of our constraints by their initial guesses. Here the goal is to make the problem equally sensitive to steps in any direction. The so-called identifiability problem of bounding uncertainty of the parameter estimates is resolved by constraining the parameter values by our experimental observations of them and their associated measurement uncertainties. Because Nelder-Mead cannot be used for explicitly constrained problems we implement the constraints by using an exterior penalty function. In the case of $q$, which we do not directly observe in experiment, we bound identifiability by using a Montecarlo bootstrap approach [WIP].

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{../figures/apparatus1.pdf}
\label{apparatus}
\caption{Schematic representation of drop jump with return and rebound from an electrically charged superhydrophobic substrate. The characteristic time and length scales $t_c$ and $y_c$ describe the time of flight and apoapse associated with the drop trajectory.}
\end{figure}

@@

We integrate Equation \ref{gov_eqn_subs} numerically using the \emph{netlib ODEPACK} library double-precision \verb|lsoda| integrator wrapped within the \verb|odeint| \emph{Scipy} \cite{oliphant_python_2007} module in Python. The optimization problem in this case is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned. The ill-conditioning arises due to the strong covariance between several of the model parameters, namely $q=q(V_d, E_0)$. The non-convexity of the problem implies that there are many local minima of the objective function. We use a gradient-free direct-search Nelder-Mead \cite{nelder_simplex_1965} algorithm implemented in \verb|scipy.optimize|. Nelder-Mead is relatively robust to noise and is thrifty with our computationally expensive function-calls. Experimental trajectory data is smoothed using a Savitsky-Golay filter \cite{savitzky_smoothing_1964} to improve the convergence characteristics of the optimizer. This filter is implemented in the \verb|scipy.signal| Python \emph{SciPy} module. We precondition the optimization problem by minimizing $\ln(\chi^2)$ and using a naive $\sim \mathcal{O}(1)$ scaling of our constraints by their initial guesses. Here the goal is to make the problem equally sensitive to steps in any direction. The so-called identifiability problem of bounding uncertainty of the parameter estimates is resolved by constraining the parameter values by our experimental observations of them and their associated measurement uncertainties. Because Nelder-Mead cannot be used for explicitly constrained problems we implement the constraints by using an exterior penalty function. In the case of $q$, which we do not directly observe in experiment, we bound identifiability by using a Montecarlo bootstrap approach [WIP].
